Component-Based mruby Platform for IoT Devices

### 2017-11-15 ipsj/paper.tex
Fix typo

For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
Therefore, applying scripting languages to embedded systems is difficult.
To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}, \cite{mrubyonTECS3}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.

>>>>

For embedded systems, real-time properties, such as estimation of worst-case execution time, are very important.
Although scripting languages are easy to use and read, their execution requires more time than that required by the codes written in C.
Therefore, applying scripting languages to embedded systems is difficult.
To address the above limitation, ``mruby on TECS,'' a component-based framework for running script programs, has been proposed \cite{par:mrubyonTECS}, \cite{par:mrubyonTECS3}.
This framework integrates two technologies, i.e., mruby, which is a lightweight implementation of Ruby for embedded systems \cite{par:mruby}, \cite{url:mruby}, and TECS, which is a component-based framework for embedded systems \cite{par:TECS}, \cite{url:TOPPERS}.
